Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)

### 2017-04-21 paper.tex
Updated a bunch of benchmarks

\item \textit{Fragmented} (``frag'' for short). This workload first allocates
$2^{19} + 2^{18}$ contiguous 4KB blocks. Then, it resizes every other block to
40KB. This represents the worst case behavior we could think of. It requires the
kernel to find a block it has not touched in over $2^{19}$ operations and move
it somewhere else.  \end{itemize}

>>>>

\item \textit{Fragmented} (``frag'' for short). This workload first allocates
$2^{20}$ contiguous 4KB blocks. Then, it resizes every other block to
16KB. This represents the worst case behavior we could think of. It requires the
kernel to find a block it has not touched in $2^{20}$ operations and move
it somewhere else.  
\end{itemize}
